Concentration

Masturbation and sex do not help concentration, when you are trying to concentrate, you automatically try and avoid distractions. Therefore, when a PMOer wants to concentrate, he doesn't even think, he automatically PMOs, feeding the little monster and partially ending the craving. Getting on with the matter at hand, he has already forgotten he has PMOed. After years of dopamine flooding the brain changes affect abilities such as accessing information, planning and impulse control.

You are also driven to provide novelty for the next PMO session as the same stuff will not generate enough dopamine and opioids, you will have to roam the internet streets for novelty, fighting the pull to cross the line towards shocking material, this in turn creates more stress, leaving you unfulfilled after finishing.

Concentration is also adversely affected due to doapmine receptors being culled due to natural tolerance to the large surges, reducing the benefit of smaller dopamine boosts from natural de-stressors. Your concentration and inspiration will be greatly boosted as this process is reduced. For many, it is the concentration aspect that prevents them from succeeding with the willpower method, they could put up with the irritability and bad temper, but the failure to concentrate on something difficult once their crutch is removed ruins many.

Loss of concentration that PMOers suffer when they try to escape is not due to the absence of sex, let alone PMO. You have mental blocks when you are addicted to something, when you have a mental block, what do you do? You fire up the browser, that doesn't cure the block so then what do you do? You do what you have to do, you get on with it, just as non-PMOers do.

When you are a PMOer nothing is blamed on the cause, PMOers never have erectile dysfunction, they just have occasional down time. The moment you stop using, everything that goes wrong is blamed on the reason you stopped. Now when you have a mental block, instread of just getting on with it, you begin to say "If only I could check my harem now, it would solve all my problems". You then begin to question your decision to quit and escape from the slavery.

If you believe that PMOing is a genuine aid to concentration, worrying about it will guarantee that you won't be able to concentrate. The doubting, not the physical withdrawal pangs, causes the problem. Always remember, it is the PMOer who suffers pangs, not non-PMOers.
