\documentclass[easypeasy.tex]{subfiles}
\chapter{Why is it difficult to stop?}

All PMOers feel that something evil has possessed them, in the early days it is a question of "I will stop, just not today", eventually getting to the stage where we that we think we haven't got the willpower or there is something inherent in PMO that means that must have it to enjoy life. PMO addiction can be compared to clawing your way out of a slippery pit, you feel that you are near the top, seeing the sunshine but finding yourself slipping down as your mood dips. Eventually opening your browser and feeling awful as you masturbate, trying to work out why you have to do it.

Ask a PMOer "If you could go back to the time before you became hooked, with the knowledge you have now, would you have started PMO?"

"NO WAY!" would be the reply.

Say to the most confirmed PMOer, someone who defends internet porn and doesn't believe that it causes injury to the brain or decreases in dopamine receptors: "Do you encourage your children to use PMO?"

"NO WAY!" is again the reply.

Porn is an extraordinary enigma, as said previously, the problem is not explaining why it is easy to stop; it is explaining why it is difficult. The real problem is explaining why anyone does it even after getting insights on neurological damage. Part of the reason we start is because of the tens of millions already into it, yet all wish they had not started in the first place, telling us it is like living life in second gear. We associate it with freedom or being "sex educated" and work hard to become hooked, spending the rest of our lives telling others not to start and trying to kick the habit ourselves.

We also spend a significant percentage of our time feeling hopeless and miserable, educating ourselves with supernormal stimulai that makes us prefer and long for these cold images, even when warm real ones are available. Living our lives as slaves to the sure and drop of dopamine induced by PMO, sentencing ourselves to a lifetime of irritability, anger, stress, fatigue and PIED. Using porn in the absence of the best parts of sex, physical touch, feel, voice, ect, we end up feeling miserable and guilty.

In fact, reading about internet pornography's addictive and destructive capabilties here and in other sites makes us more nervous and hopeless! What sort of hobby is it that when you are doing it you with you weren't and when you aren't you crave for it? Despising themselves reading about hypofrontality and densensitisation, PMOing behind their trusting partners back and unable to pull themselves up to exercise after a daytime PMO. A lifetime of an otherwise intelligent and rational human going through life in contempt. Having to go through through life with these awful black shadows at the back of his mind, what do they get out of it? \textbf{Absolutely nothing!}

You might be thinking "That's all very well, I know this, but once you are hooked on these things it is very difficult to stop." But why is it so difficult? Some say that it is because of the powerful withdrawl symptoms, but as you will come to learn the actual dopamine withdrawl symptoms are so mild that PMOers should know about smokers who have lived and died without realising they are drug addicts.

Some say that internet porn is free and humankind should claim this biological bonanza, this is untrue, it is addictive and acts like any other drug. Ask a PMOer that swears they only enjoy playboy type erotica, if they are absolutely honest, you would hear about all of the times they have unwittingly crossed the line. Rather using 'unsafe' porn and rationalising it than being left using nothing at all.

Enjoyment has nothing to do with it either, I enjoy crayfish but I never got to the stage where I needed crayfish multiple times or everyday. With other things in life we enjoy them whilst we are doing them, but we don't sit feeling deprived when we are not.

Some say:
  "It is educational!" - So when is your graduation?
  "It is sexual satisfaction!" - So why do it alone instead of finding a partner and saving it for them?
  "It is a feeling of release!" - Release from the stresses of real life? Porn will not remove the source of the stress, in fact, it will add to it.

Many believe that PMO relieves boredom, this is also a fallacy as boredom is a frame of mind. Porn will introduce you to novelty seeking in no time, causing you to become increasingly bored until you participate in the wild goose chase for the right clip to hit your dopamine receptors, increasingly wired to find clips that evoke strong emotions, novelty and outrageous shock value.

Some only do it because their friends and everyone they know do it. If so, hope that your friends do not start cutting their heads off to cure a headache! Most users who think about it end up coming to the conclusion that it is just a habit, generally coming to this conclusion through elimination of the usual explanations. Unfortunately, this explanation is equally illogical. Every day we change habits, some of them being very enjoyable. We have been brainwashed to believe that PMO is a habit and habits are difficult to break.

Are habits actually difficult to break? Drivers in the US are in the habit of driving on the right side of the road, but travelling overseas to Australia, drivers break the habit with hardly any aggravation whatsoever. It is clearly a fallacy that habits are hard to break, so why do we find it difficult to break a habit that makes us feel deprived when we don't have it, guilty when we do and one that we would love to break anyway, when all we have to do is stop doing it?

The answer is that PMO is not a habit, \textbf{IT IS ADDICTION!} That is why it appears to be so difficult to 'give up', most PMOers do not understand addiction and believe that they get some genuine pleasure or crutch from porn and believe they are making a genuine sacrifice if they quit.

The beautiful truth is that once you understand the true nature of porn addiction and the reasons why you PMO, you will stop doing it just like that. Within three weeks, the only mystery will be why you found it necessary to PMO as long as you have and why you cannot persuade other PMOers of \textit{how nice it is to be a non-PMOer!}
