Boredom

If you are like many people, as soon as you get into bed you are already on your favorite porn site, you will have probably already forgotten about this until you were reminded. It has become second nature. PMO relieving boredom is another fallacy, boredom is a frame of mind. The only time this happens is when you have been deprived for a long time or are trying to cut down.

The actual situation is this, when you are addicted to the supernormal pull of internet porn and then try to abstain, there is something missing. If you have something to occupy your mind that isn't stressful, you can go for long periods of time without being bothered by the absence of the drug. However, when you are bored there is nothing to take your mind off it, so you feed the monster. When you are indulging yourself, not trying to stop or cut down, even firing up private browsing becomes subconscious. The PMOer performs this ritual automatically, if he tries to remember sessions during the last week, he can only remember a small proportion of them, like the very last one or after a long abstinence.

The truth is that PMOing increases boredom indirectly because orgasms make you feel lethargic and instead of undertaking an energetic activity, PMOers tend to prefer lounging around, bored, relieving their withdrawal pangs. Countering the brainwashing is important because PMOers tend to PMO when they're bored, our brains wired to interpret PMO as interesting. Similarly, we've also been brainwashed into beleiving sex, even bad sex, aids relaxation. It is a fact that when sad or under stress, couples want to have sex. In the absense of discrimination between amative and propagative sex, watch how quickly you want to get away from each other after the mandatory orgasm is achieved. If the couple had just decided to hug, speak or cuddle and go to sleep, they would have felt relieved.
