Stress

Not only great tragedies in life, but also minor stresses drive the PMOer one step further into the forbidden area previously excluded. Stresses includes socialising, phone calls, anxieties of the housewife with young children and many others. Taking take phone calls as an example, particularly for a businessperson. Most calls aren't from satisfied customers or your boss congratulating you, there's some sort of aggravation. Coming home to mundane family life of kids screaming and their partners emotional demands the PMOer, if they aren't already doing so, will fantasise the relief of porn promised that night. Unconsciously suffering withdrawal pangs, weakened de-stressors unprepared for the additional aggrevation. Partially relieving the pangs at the same time as normal stress, the total is reduced and the PMOer gets a temporary boost. The boost isn't an illusion, the PMOer does feel better than before, but they are more tense than they would be as a non-PMOer.

The following example isn't designed to shock you, EASYPEASY promises no such treatment, but is to emphasise that PMO destroys your nerves rather than relaxing them.

Try to imagine getting to the stage where you are unable to be aroused, even with a very sexy and attractive partner. For a moment, pause and try to visualise life where a very lovely and charming person has to compete and fail with the virtual porn stars who occupy your 'harem' to get your attention. Imagine the frame of mind of a person, who issued with that warning, continues PMOing and dies without ever having real sex with this charming and willing partner. It's easy to dismiss these people as weirdos but stories like these are not fakes, this is what the awful novelty of the porn drug does to your brain. The more you go through life, the more your courage is sapped and the more you are deluded into the believing porn is doing the opposite.

Have you ever been overtaken by panic when out of the blue the WiFi stops working or is too slow? Non-PMOers do not suffer from it, the internet porn drug causes that feeling. As you go through life, it systematically destroys your nerve and courage, leaving Delta-FosB to form a powerful neural water slide in it's wake, progressively destroying your ability to say no. By the stage where virility has been killed, the PMOer believes the PMO is his new partner and is unable to face life without it.

Internet porn is not relieving your nerves, it is slowly destroying them. One of the great gains of breaking the addiction is the return of your natural confidence and self assurance.

There is no need to self-rate based on your ability to satisfy a partner, this is not freedom. But this freedom cannot be obtained by continuing to grease the dopamine water slide in ways that undercut your happiness and libido by repeating the same destructive behaviour.
