What am I giving up?

\textbf{Absolutely nothing!} PMO is difficult to give up because of fear we are being deprived of our pleasure or prop. The fear that certain pleasant situations will never be quite the same again. The fear of being unable to cope with stressful situations. In other words, the effects of brainwashing to delude us into believing that sex and by extension, orgasm, is a must for all human beings. Even further, believing there is something inherent in internet porn that we need and that when we stop PMOing we will be denying ourselves and creating a void.

Make this clear in your mind:
  \huge{Internet Porn does not fill a void, it creates one!}

Our bodies are the most sophisticated objects on the planet. Whether you believe in intelligent design, natural selection or a combination of both, our bodies are a thousand times more effective than man! We are unable to create the smallest living cell or the miricles of eyesight, reproduction, various interlinked systems present in our bodies or brains. If this creator or process had intended us to handle supernormal stimulus, we would have been provided with a different reward system. Our bodies are provided with fail-safe warning devices, ignoring these at our peril.

There is nothing to give up
Once you purge the little monster from your body and the brainwashing (the big monster) from your mind, you will neither want to masturbate often or need internet porn for it. There are many knowns and unknowns when it comes to porn addiction, many in the medical community have no concept of questioning and determining someone as a porn addict. A lot of reported symptoms are wrongly tagged other causes. It's not that PMOers are generally stupid people, it's just that they are miserable without PMO. They are caught between the devil and the deep sea, abstaining and being miserable because they cannot PMO or miserable because they are guilty and begin despising themselves because of it. When they get symptoms such as lower back pain or PIED, their minds are torn between accepting responsibility and looking the other way.

Another smoker analogy, all of us have seen smokers who develop excuses to sneak off for a crafty puff, it is easy to see the true addiction in action. Addicts do not do it because they enjoy it, they do it because they are miserable without it.

For many their first sexual experience ended in an orgasm, so they acquired the belief that they cannot enjoy sex without one. For men, porn is marketed as an aid towards sex, sometimes even as an education in confidence during the act. This is nonsense, the conditioning of supernormal stimulus only succeeds in bringing it down.

Not only is there nothing to give up, but there are massive positive gains to be had. When PMOers contemplate quitting, they tend to concentrate on health and virilty, these are valid and important reasons, but I personally believe the greatest gains are psychological:
  The return of your confidence and courage
  Freedom from slavery
  No longer having awful black shadows at the back of your mind, despising yourself

Void, the void, the beautiful void!
Imagine having a cold sore on your face, you go to the pharmacist and he gives you a free ointment to try. You run the ointment on and it disappears immediately. A week later it reappears.
  "Do you have any more of that ointment?"
The pharmacist says "Sure, keep the tube, you might need it later."
You apply the ointment once again, hey presto, the sore disappears once again. But every time the sore returns, it get larger and more painful, with the interval getting shorter and shorter. Eventually, the sore covers your whole face and is excruciatingly painful, it's now returning every half hour. You know the ointment will remove it temporarily, but you are very worried. Will the sore eventually spread over your whole body? Will the interval disappear completely? You go to your doctor, he can't cure it, you try other things but nothing helps apart from the ointment.

By now you are completely dependent on the ointment, never going out without ensuring that you have a tube with you. If you go abroad, you make sure you take several tubes with you. In addition to your worries about your health, the pharmacist is charging you a hundred dollars a tube. You have no choice but you pay up.

You stumble across an article discussing this and find out it isn't just happening to you, many people are suffering from the same problem. In fact, the medical community has discovered that the ointment doesn't actually cure the sore, all that it does is take the sore beneath the surface of the skin. It's the ointment that caused the sore to grow, all you have to do to get rid of the sore is to stop using the ointment, it will disappear in due course.

Would you continue to use the ointment? Would it take willpower to not use the ointment? If you didn't believe the article, there might be a few days of apprehension, but once you realised the sore was beginning to get better, the need or desire to use the ointment would go. Would you be miserable? Of course you wouldn't! You had an awful problem which you thought was incurable, now you've found the solution. Even if it took a year for the sore to go away, every day as it improved, you'd think about how marvellous you felt. This is the magic of quitting PMO.

The sore isn't the body pains, lack of normal lust, flagging arousal, fading penetration, wasted time spent on two-dimensional images, feelings of infringement on entitlement, despising the people who caught you, or even worse, despising yourself. These are all in addition to the sore.

The sore makes us close our minds to all these things, it's that panic feeling of wanting a fix. Non-PMOers don't suffer from that feeling. The worst thing we ever suffer from is fear, the greatest gain being rid of that fear. It is caused by your first PMO session, further strengthened and caused by each subsequent one.

Some PMOers are 'happy', blinded by their cunning little monsters, are going through this same nightmare, putting up phony arguments to try and justify their stupidity.

\textif{It's so nice to be free!}
