Social Night PMOing

This is misinformation that seems to make sense, but it doesn't. In order to control your appetite, will you eat at home before leaving to go to a restaurant or party? This is what you are doing when you PMO before your social night, you will look tired and will not be up to your best. The widespread adoption of pick-up techniques has introducted pressure to perform, pick-up and score. Attempting to drown your butterflies with PMO and substances will only make the problem worse in the long run. Personally, I like a bit of anxiety to keep me focused and engaged, tiring yourself out mentally and physically with orgasm is not going to help.

Social night PMOing is occasioned by two or more of our usual reasons for pleasure/prop seeking, social functions are at their core both stressful and relaxing. This might appear to be a contradiction but any form of socialisation can be stressful, even with friends. At the same time however, you want to be yourself and completely relaxed. There are many occasions that have multiple factors present at any one time, take driving as an example, after all, your life is at stake. Stressful with concentration required for a sustained period of time, you need not be aware of these factors, your subconscious has already got the message. By the same token, stuck in traffic jam or bored on a long highway drive, you might have promised yourself a PMO when you reach home.

Another good example is going on a first date, your mind throwing out questions about the person you are about to meet. Then you meet the person in the flesh, if your enthusiasm starts to fade you will start to feel too relaxed, then feeling guilty for feeling this way. The tug of war has started, I want sex or get me out of here ASAP, priming you post date PMOing.

Even if the date went well and hours later you are back at her place, no matter which way it goes you will not be satisfied if your only goal is seeking orgasm. At other times, you drive home alone, only thought being your online harem instead of patting yourself on the back for your efforts. You can bet that someone in this position will PMO when they reach home, it is often after nights like these, when we wake to feel uneasy emptiness, are the ones we will miss the most when we are contemplating stopping PMOing. We think that life will never be quite as enjoyable again. In fact, it is the same principle at work, the PMO sessions simply provide relief from the withdrawal pangs, at some times having greater needs than others. Greasing the water slide for the next cue.

Make this clear - It is not the internet porn and harem dwellers that are special, it is the occason. Once the need for PMO is removed, such occasions will become more enjoyable and stressful situations less stressful.
