\documentclass[easypeasy]{subfiles}
\chapter{Casual PMOers, Teenagers, Non-PMOers}
\begin{document}

Heavy PMOers tend to envy the casual porn user, we've all met these characters \textit{"Oh, I can go all week without a PMO, it doesn't really bother me."} We wish we were like that. This might be hard to believe, but no PMOer enjoys being a PMOer. Never forget:

  No PMOer ever decided to become a PMOer, casual or otherwise, therefore,\\
  All PMOers feel stupid, therefore,\\
  All PMOers have to lie to themselves and others in a vain attempt to justify their stupidity.

Golf fanatics brag about how often they played and want to play. Why do PMOers brag about how little they masturbate? If that's the true criterion, then surely the true accolade isn't masturbating at all?

If someone said to you, \textit{"I can go all week without carrots and it doesn't bother me in the slightest"}, you'd think you were talking to a nutcase. If I enjoyed carrots, why would I want to go all week without them? If I didn't enjoy them, why would I make such a statement? So when a user makes a comment about surviving a week without a PMO session, they're trying to convince both themselves and you that they don't have a problem. But there would be no need to make a statement if they didn't have problem. Translated, this comment is \textit{"I managed to survive a whole week without PMOing."} Like every PMOer, hoping that after this they could survive the rest of their lives. Only able to survive a week, can you imagine how precious the PMO session must have been afterwards, having felt deprived for an entire week?

This is why casual PMOers are effectively more hooked than heavy PMOers, not only is the illusion of pleasure greater but they have less incentive to quit because they spend less time and are therefore less vulnerable to the health risks. They may occasionally experience PIED, but are unsure what caused it, blaming it on other factors. Remember, the only pleasure PMOers get is in the search-and-seek dopamine cycle and relieving the withdrawal pangs, as has already been explained. The pleasure is an illusion, imagine the little porn monster inside your body as a near imperceptible itch that we're unaware of most of the time.

If you have a permanent itch, the natural tendancy is to scratch it. As the brain's reward circuits become increasingly more immune to dopamine and opioids, the natural tendency is to edge, escalate, binge, novelty-seek, shock-seek, ect. There are four main factors that prevent PMOers from chain-PMOing.

  \begin{description}
  \item [Time.] Most cannot afford to.
  \item [Health.] In order to relieve the itch, we have to consume all free material that's available and then some. Capacity to cope with that kind of binging varies with each individual at different times and situations in their life. This acts as an automatic restraint.
  \item [Discipline.] Imposed by society or the PMOers job, friends and relatives, or even the PMOer themselves as a result of the natural tug-of-war that goes on in every PMOers mind.
  \item [Imagination.] Lack of imagination plays down the shock, novelty and other values of the clip on a subjective basis.
  \end{description}

It's easy to think of 'non-casual' PMOing as weakness, unable to understand why others are able to limit their 'intake'. However, the heavy PMOer should keep in mind that most casual PMOers are simply incapable of chain-PMOing, needing a very strong imagination and stamina in order to accomplish it. Some of these once-a-week PMOers that heavy PMOers tend to envy are physically unable to do more, or because their job, society or their own hatred of becoming hooked won't allow them to do more.

It may be advantageous to provide a few definitions.
 \begin{description} 
   \item [The Non-PMOer] Someone who has never fallen pray to the PMO trap but shouldn't be complacent. They're a non-PMOer only by luck or grace of goodness. All non-PMOers were convinced they'd never become hooked, some non-PMOers keep trying an occasional session.

   \item [The Casual-PMOer] There are two basic classifications of casual PMOers
\begin{enumerate}
\item The PMOer who's fallen for the trap but doesn't realise it, don't envy such PMOers. They're merely sampling the nectar at the mouth of the pitcher plant and in all probability will soon be heavy users. Remember, just as all alcoholics started off as casual drinkers, so too all PMOers started off as casual PMOers.

\item The PMOer who was previously a heavy PMOer and thinks they can't stop. These PMOers are the saddest of all, they fall into various categories, each of which needs separate comment.
\end{enumerate}
    \item [The Once-a-Day PMOer] If they enjoy their entitlement to orgasm, why use internet porn only once a day? If they can take it or leave it, why bother to PMO at all? Remember, the 'habit' is in actuality banging your head against a wall to make it relaxing when you stop. The once-a-day PMOer is relieving their withdrawal pangs for less than an hour each day. Although they don't realise it, the rest of the day is spent banging their head against the wall, doing this for most of their lives. They're PMOing once a day because they cannot risk getting caught or messing with their neurological health. It's easy to convince the heavy PMOer they don't enjoy it, but significantly harder to convince a casual PMOer. Anyone who has gone through an attempt to cut down will know it's the worst torture of all and almost guaranteed to keep you addicted for the rest of your life.

    \item [The Rejected PMOer] The PMOer demands the right to their orgasm every day, but their sex partner isn't always happy to fulfill their request. Intially, they use internet porn to fill this void, but once they take the exciting 'water slide' they're trapped in a cycle of novelty, shock, supernormal images, ect. They're in fact happy with their partners rejection, providing something of an excuse. If internet porn is giving so much to you, why bother to have a partner at all? Set them free instead. They're not even enjoying the PMO sessions when they have to 'carry' their partner in their mind. At some point, they're using their real life partner to hand them an excuse to go out into the valleys of the dark side of the internet.

    \item [The Porn Diet PMOer] Also known as, \textit{"I can stop whenever I want to. I've done it thousands of times!"}\\ If they think dieting helps with mood to pick up partners, why are they even on the diet of once in every four days? Nobody can predict the future, what if the happenstance of meeting occurred an hour after your scheduled PMO session? Also, if the occasional 'cleaning the plumbing' is good to relieve tension, why not plumb every day? It's been proven that masturbation isn't required to keep genitals healthy, internet porn isn't required at all. Even if that's the case, any pick-up-artist 'guru' who has read about the neurochemistry will ever recommend watching super-stimulus porn. The truth is, they're still hooked. Although they're rid of the physical addiction, still let with the main problem, the brainwashing. They're hoping each time they will stop for good, but soon fall for the same trap again.

  Most PMOers actually envy these stoppers and starters, thinking about how 'lucky' the dieter is to be able to control their usage. However, what they overlook is that the dieter isn't controlling their usage, when they're PMOers, they wish they weren't. They go through the hastle of stopping, then begin to feel deprived and fall for the trap again, wishing they hadn't. They get the worst of both worlds. If you think about it, this is true in the lives of the PMOers, when allowed to PMO, taking it as entitled or wishing they didn't. It's only when they're deprived that PMO is precious. The 'forbidden fruit' syndrome is one of the awful dilemma of PMOers. They can never win because they're moping for a myth, an illusion. There's only a single way they can win, stopping moping by stopping PMO!

\item [The "I Only PMO to Static/Tame/Home-Made Porn PMOer"] Yes, we all do this to start with, but isn't it amazing how the average shock value of these clips seems to rapidly increase and before we know it we seem to be feeling deprived (tolerance)? The novelty is lacking with static porn, so we pay the piper for a cup of grease and ride down the water slide towards resentment and guilt. The worst thing you can do is use your partners pictures (with approval, of course) for masturbation. Why? Because in the process you're re-wiring your brain for the seeking, searching and variety induced dopamine flushes. The porn water slides in your brain is DeltaFosB building up, so you'll find yourself having difficulties when you're with them in real time.

  Another trap in this category is 'amateur' and 'home-made' porn. Most are fakes and you know it, you're also not going to stop at the very first one that hits your eyes, continuing to seek and search. Remember, it's not only orgasm the brain seeks, but the novelty of the hunt that gives the water slide the thrill. The porn content isn't the issue, whether amateur or professional, it's the flushes of dopamine in the brain that causes the build up of tolerance and satiation. Porn destroys normal brain operation, masturbation confusing the muscle-brain response. Orgasm flooding the brain with opioids and making the pathway easier to follow next time.

\item[The "I have stopped but have an occasional peek" PMOer] In a way, peeking PMOers are the most pathetic of all. Either they go through their lives believing they're being deprived, or more often, the occasional peek becomes two. They remain on the slippery slope, sliding downwards, sooner or later back to being heavy PMOers. They've again fallen for the very trap they fell into in the first place.
 \end{description}

There are two other categories of casual PMOers. The first is the type that masturbates to images or clips of the latest celebrity sex tapes that hit the news, or something they 'carried home' from their 'accidental' viewing at school or work. These people are really just non-PMOers, but feel that they're missing out. They want to be part of the action, most of us starting off this way. Next time, notice that after a while, the celebrity of your fantasy isn't doing it for you anymore. The more 'unattainable' the target of your fantasy is, the more frustrating the withdrawal of the orgasm is.

The second category has been gaining attention recently, best described by outlining a case shared online. A professional woman had been reading internet porn stories for many years and had never PMOed more or less than once each night. She was, incidentally, a very strong willed lady. Most PMOers would wonder why she wanted to stop in the first place, gladly pointing out that there wasn't any risk of PIED, or PE in her case (untrue). She wasn't even using static images, the stories being far tamer than any themselves use on a daily basis.

They make the mistake of assuming that casual PMOers are happier and more in control. They might be more in control, but certainly not happy. In the woman's case, she wasn't satisfied with her partner, nor real sex and highly irritiable responding to her daily stresses and strains. Her nearest-and-dearest was unable to figure out what was bothering her. Even if she convinced herself to be unafraid of her internet porn usage through rationalisation, still finding herself unable to enjoy real relationships which invariably involve ups and downs. Her brain's reward centre is unable to make use of normal de-stressors present in life as she's flooding dopamine on a daily basis. Subequent down regulation of her brain's receptors had rendered her melancholic under most circumstances. Like most, she had a great fear of porn's dark side and treatment of women - before her first time. Eventually falling victim to the societal brainwash and trying her first site, seeing the foul clips of violence staged as entertainment. Unlike most, who capitulate and become chain-PMOers, she resisted the slide.

All you ever enjoy in PMO is the ending of the craving that started before it, whether the almost imperceptible physical craving or the mental torture of not being allowed to scratch the itch. Internet porn itself is a poison, which is why you only suffer the illusion of enjoying it after a period of abstinence. Similar to hunger or thirst, the longer you suffer it, the greater the pleasure when you finally relieve it. Making the mistake of believing PMO is just a habit, they think: \textit{"If I can keep it down to a certain level or only on special occasions, my brain and body will accept it. Then, I can keep my PMOing at that level or reduce it further should I wish to."} Get it clear in your mind, the 'habit' doesn't exist. PMOing is drug addiction, the natural tendency being to relieve withdrawal pangs, not to endure them. To hold it at the level you're currently at would require you to exercise tremendous amounts of discipline and willpower for the rest of your life, because as your brain's reward centre becomes immune to dopamine and opioids, it wants more and more, not less and less. 

As PMO begins to gradually destroy your nervous system, your courage and confidence and impulse controls, you become increasingly unable to resist reducing the interval between each session. This is why in the early days, we can take it or leave it. If we get a sign of something amiss mentally or physically, we just stop. Don't envy this woman, when you PMO only once every twenty-four hours it appears to be the most precious thing on earth, turning PMO into a 'forbidden fruit'. For many years this poor woman had been at the centre of a tug of war.

Unable to stop PMOing, yet frightened to escalate to streaming clips. For twenty-three hours and ten minutes of every one of those days she had to fight the temptation and having to fight her lack of feelings towards her boyfriend. It took tremendous willpower to do what she did, reducing her to tears in the end. Such cases are rare, but look at it logically: Either there's a genuine crutch or pleasure in PMOing or there isn't. If there is, who wants to wait an hour, a day, or a week? Why should you be died the crutch or pleasure in the meantime? If there's no genuine crutch or pleasure, why bother paying a visit to your online harem?

  Here is another case of a once-in-four-days man, describing his life as follows:\\

  \textit{"I am forty years old, I suffered PIED with real women and even when I'd be PMOing. Most times I'm only rubbing it out. It's been a while since I had a full erection, before going on the once-in-four porn diet, I used to sleep soundly through the night after my PMO. Now I wake up every hour of the night and all I can think about is PMO. Even when I'm sleeping, I dream about my favorite clips. On days after my scheduled PMO I feel pretty down, the diet taking up all of my energy. My SO would leave me alone because I'm so bad-tempered and if she can't get out, she won't have me in the house. I go for a jog outside but my mind is obsessed with PMOing. On the scheduled day I begin planning earlier in the night, getting very irritated if something happens against my plans. I'd give up on conversation and give in (only to later regret) at work and home. I'm not an argumentative guy, but I don't want the topic or conversation to hold me down. I remember occasions when I'd pick silly fights with my SO. I then wait for ten o'clock, when it arrives my hands are shaking controllably. I don't start the deed right away, as there are new videos that have been added, I 'shop around'. As I click around, my mind tells me that since I've starved myself for four days I deserve a 'special' clip that has to worth the time spent searching. Eventually I settle for one or two, but want it to last so that I can 'survive' through the next four days, so I take more time to finish the deed."}\\

In addition to his other troubles, this poor man has no idea that he's treating himself to a poison. Firstly, suffering 'forbidden fruit syndrome' and then forcing his brain to flush dopamine. Comparatively, his dopamine receptors aren't as cut down, but he's greasing the porn water slides, seeking, searching for edging, novelty, variety, shock and anxiety in order to survive the next four days. You probably picture this man as a pathetic imbecile, but this isn't so. A former athlete turned ex-marine sergeant and didn't want to become addicted to anything. However, upon returning from war he trained as an IT technician in a veterans rehab program. When he entered the civil work-force, he was a well paid IT professional in a bank and was given a laptop to take his work home. It was the year where the famous socialites 'leaked' their porn videos online and there was much talk about it. Then he got hooked, spending the rest of his life paying through the nose, ruining him physically and mentally. If he was an animal, society would have put him out of his misery long ago, yet we still allow mentally and physically healthy young teenagers to become hooked. You may think the case and notes are exaggerated, but this case while extreme is far from unique. There are tens of thousands of similar stories. Can you be sure that many of his friends and acquaintances envied him for being a once-a-week man? If you think this couldn't happen to you, \textbf{stop kidding yourself.}

{\huge IT'S ALREADY HAPPENING.}

PMOers like other addicts, are notorious liars, even to themselves. They have to be. Most casual PMOers indulge far more times and on far more occasions then they'll admit to. Many conversations with so called twice-a-week PMOers will admit they've done it more than three or four times that week. Read reddit, NoFap and rebooting forum stories from casual PMOers and find they're either counting days or waiting to fail. You don't need to envy casual PMOers, you don't need to PMO either, life is infinitely sweeter without it. Take the following log:

  \textit{"It started with a simple challenge to not touch my penis for a day and being unable. I don't think about masturbation anymore, it doesn't cross my mind. That is possible, I promise you. The riches that await those who are able - they're incredible."}

Teenagers are generally more difficult to cure, not because they find it more difficult to stop, but because they don't believe they're hooked or are at the primary stage of the trap and suffer from the delusion they'll automatically have stopped before the second stage.

Parents of children who loathe internet porn shouldn't have a false sense of security. All children loathe the dark sides of porn before they become hooked. At one point, you did too. Do not be fooled by scare campaigns either, the trap is the same as it always was. Children know that internet porn is supernormal stimulai, but they also know that one 'visit' or 'peek' won't do it. At some stage they may be influenced by a partner, classmate or work colleague.

You may think that all they need is an education in brain plasticity and that PMO (even including masturbation) acts like a virus in their brain to convince them they could never become hooked. Societies failure to prevent adolescents from becoming addicted to internet porn and other drugs is perhaps the most disturbing of all of the many facets of addiction. I beg you not to become complacent in this matter, it's necessary to protect adolescents as their brain is more plastic at their age. A good resource is the YourBrainOnPorn book and educating yourself of the neuroscience. Even if you suspect that your teenager might already be hooked, the book with provide excellent guidance to assist in gaining understanding to help someone to escape.
\end{document}
