Relaxation

Most PMOers think that PMO helps to relax them, it does not. The frantic search to get the fix in those 'dark alleys of the internet' and the internal struggle straining at the leash to cross the red line does not sound like a very relaxing activity.

As night rolls in, after a trip to a new place or a long day, we sit down and relax, relieve our hunger, thirst and are completely satisfied. The PMOer is not, having another hunger to satisfy. He thinks of the PMO as the icing on the cake, but it is the 'little monster' that needs feeding. The truth is that the addict can never be completely relaxed and as you go through life it gets worse.

Take one onlne comment from an ex-PMOer
  \textit{"I really believed that I had an evil demon in my make up, I now know that I had, however it wasn't some inherent flaw in my character but the little internet porn monster that was creating the problem. During those times I thought I had all the problems in the world, but when I look back on my life I wonder where all the great stress was. In everything else in my life I was in control, the one thing that controlled me was porn slavery. The sad thing is that even today I can't convince my children that it was the slavery that caused me to be so irritable."}

Every time I hear a porn addict trying to justify their addiction the message is, "Oh it helps me to relax." On the internet I read about a single dad whose six year old son would want to share his bed in the night after a scary movie, but the dad would refuse so that he could have his PMO session and edge for hours.

Here's another smoking analogy, a couple of years ago adoption authorities threatened to prevent smokers from adopting children. A man rang up, irate. "You are completely wrong", he said "I can remember when I was a child, if I had a contentious matter to raise with my mother, I would wait until she lit a cigarette because she was more relaxed then." Why couldn't the man talk to his mother when she wasn't smoking a cigarette?

Why are some PMOers are so stressed when they are not getting their fix, even after real sex? One story online details a man working in the advertising field having 9's and 10's open for dates at any time, but he lost interest in taking them out for dinner as internet porn was far easier for him, no resturant spending and the possibilty of a 'no' from his date at the end of an evening. Why would be bothered when his little monster keeps him craving the low risk, high reward scheme at his fingertips when he reaches home?

Why are non-PMOers competely relaxed then? Why are PMOers not able to relax without a fix for a day or two? Read about the experience of a PMOer taking the abstinence oath and quitting and you will notice the struggle with temptations, clearly not relaxed at all when not allowed to have the 'only pleasure' they are 'entitled to enjoy'. They've forgotten what it's like to be completely relaxed. PMOing can be likened to a fly being caught in a pitcher plant, to begin with, the fly is eating the nectar but at some imperceptible stage the plant begins to eat the fly.

Isn't it time you climbed out of the plant?

