\documentclass[easypeasy.tex]{subfiles}
\chapter{The YouTube PMOer}
\begin{document}

The YouTube PMOer should be grouped with casual PMOers, but the effects of a YouTube PMOer are so insidious that it merits a separate chapter. Leading to the breakdown of self-control, nearly causing a split for one NoFap forum user:

\textit{"I was three weeks into one of my failed attempts to stop, the attempt had been triggered by my wife's worry about my unreliable hard-ons and lack of interest. I had told her that it wasn't her, just job pressure. She said, "I know you've handled the work pressure before, but how would you feel if you were me and had to watch someone you love systematically destroying themselves?" It was an argument I found irresistible, hence the attempt to stop. She knows I'm not cheating, but this in a way worse than that. The attempt ended after three weeks with a heated argument with an old friend. It didn't register until years after that my devious mind had deliberately triggered off the argument, I felt justifiably aggravated at the time but I don't believe it was coincidence as I had never argued with this particular friend before, nor have I since. It was clearly the little monster at work.}

\textit{Regardless, I had my excuse. I desperately needed a release and it didn't matter how. My wife wasn't in the mood and I was in a feeling of 'entitlement', so I convinced myself that it would be okay if I 'restricted' myself by avoiding porn sites and stay this side of the 'red line' by only watching YouTube videos. But my wife ended up 'coming around' as the night unfolded and wanted to make love, however I was tired and without my 'horsepower' so invented a headache. I couldn't bear to think of the disappointment this would cause my wife. Then I gradually returned to old ways, with YouTube becoming my new harem destination. I remember being quite pleased at the time, thinking that it was at least cutting my consumption down. Eventually, she accused me of continuing to ignore her in bed. I hadn't realised it, but she described the times I had caused an argument and stormed out of the house. At other times, I had taken two hours to purchase some minor item and faked a sprain or something. I had made feeble excuses to cop out of wooing her, when I have a reliable online harem it's even harder."}

The worst thing about the YouTube PMOer is that it supports the fallacy in the PMOers mind that they're being deprived. At the same time, it causes a major loss of self-respect; an otherwise honest person may force themselves to deceive their loved one. It's probably happened or still happening to you in some form.

Problems faced with websites like Twitch and Instagram are primarily driven by supplementation. Driven by novelty seeking dopamine urges, tricking themselves into believing they're on a safe site. Remember, the thrill is in the seeking, not the killing and the little monster doesn't care where it's fix comes from. For the PMOer, the 'soft' content received in their various online feeds gives them fleeting relief of their withdrawal pangs, keeping them hooked and waiting for their session.

You might have watched the TV series Columbo, the theme of of each episode is similar. The villain, usually a wealthy and respected businessman has committed what he is convinced is the perfected murder and his confidence in his crime remaining undetected receives a boost when he discovers that the rather shabby and unimpressive-looking Detective Columbo is in charge of the case.

Columbo has this frustrating practise of closing the door after finishing his interrogation, having assured the suspect that he is in the clear and just before the satisfied look his disappeared from the murderers face, Columbo reappears, saying \textit{"Just one small point, sir, which I'm sure you can explain..."} The suspect stammers and from that point on we know and he knows that Columbo will gradually wear him down. No matter how heinous the crime, from that point on the sympathies were with the murderer.

These bouts are similar, the tension of not being allowed to cross the red line to get the porn fix that they 'rightly deserved', then wondering where the pleasure was after finishing the deed. The fear of crossing the line and losing control, returning to the bed, only to be stalked by the fear that your partner wanted sex. As for 'safe' Youtube videos that no longer satisfy you due to densensitiation, lack of novelty and the certain knowledge that sooner or later you will visit your favorite online harem. The final humiliation and shame being when that certainty become a fact, followed by the immediate return to chain-PMOing.

{\huge OH, THE JOYS OF BEING A PMOer!}
\end{document}
