\documentclass[easypeasy.tex]{subfiles}
\chapter{Just One Peek}
\begin{document}

"Just one peek" is a myth that you must remove from your mind:
\begin{itemize}
  \item It's just one peek that gets us started in the first place.
  \item It's just one peek to tide us over a difficult patch or on a special occasion that defeats most of our attempts to stop.
  \item It's just one peek that, when PMOers have succeeded in breaking the addiction, sends them back into the trap. Sometimes it's just to confirm that they don't need them anymore and one harem visit does just that.
\end{itemize}
The after effect of PMO will be horrible and convinces the PMOer they'll never become hooked again, but they already are. The PMOer feels that something that's making them so miserable and guilty shouldn't have made them do it, yet they did.

It's the thought of 'one special PMO' session that often prevents users from stopping, the one after your long conference trip, hard day at work, fight with kids or incident where your partner rejects you for sex. Get it firmly in your mind that there's no such thing as 'just one peek'. It's a chain reaction that will last the rest of your life unless you break it. The myth about the odd, special occasion that keeps PMOers moping when they stop. Get into the habit of never seeing the 'no big deal' session, it's a fantasy. Whenever you think about porn or PMO, see a filthy lifetime of spending eons of time behind a screen for the privilege of destroying yourself mentally and physically, a lifetime of slavery and hopelessness. It isn't a crime if your erections are unreliable, but it is when you could be happier in the long term but choose to sacrifice that for short term 'pleasure'.

It's okay that we can't always come up with 'something to do' for the void, it isn't realistically possible to do that every time for our entire lives. We can plan for most of them, but sometimes it just happens. Good and bad times also happen, irrespective of PMO. But get it clearly into your mind, the PMO isn't it. You're stuck with either a lifetime of misery or none at all, you wouldn't dream of taking cyanide just because you liked the taste of almonds, so stop punishing yourself with the occasional 'no big deal' PMO. Ask a PMOer with issues, \textit{"If you had the opportunity to go back to the time before you became hooked, would you have become a PMOer?"} The answer is inevitably, \textit{"You've got to be joking!"} Yet every PMOer has that choice every day of their life, why don't they opt for it? The answer is fear. The fear that they can't stop or that life won't be the same without it.

Stop kidding yourself! You can do it, anybody can. It's ridiculously easy, in order to make it easy, there are certain fundamentals to get clear in your mind.

\begin{enumerate}
  \item There's nothing to give up, only marvellous positive gains to achieve.
  \item Never convince yourself of the odd "no big deal" or "just one peek" PMO. It doesn't exist. There's only a lifetime of filth and slavery.
  \item There's nothing different about you, any addicted PMOer can find it easy to stop.
\end{enumerate}

Many PMOers believe that they're confirmed addicts or have addictive personalities. This usually happens as a result of reading excessive amounts of shocking brain science. there's no such thing, nobody is born with a need to masturbate to video clips before they became hooked on the drug. It's the drug that hooks you, not the nature of your character or personality. The nature of addictive supernormal stimulai makes you believe this is the case. However, it's essential that you remove this belief because if you believe you are addicted, you will be, even after the little monster in your body is long dead. It's essential to remove all of this brainwashing.
\end{document}
