\documentclass[easypeasy.tex]{subfiles}
\chapter{The Withdrawal Period}
\begin{document}

For up to three weeks after your last PMO session you may be subjected to withdrawal pangs, these consist of two quite separate factors.
\begin{enumerate}
  \item Dopamine withdrawal pangs, that empty, insecure feeling, like a hunger, which PMOers identify as a craving or 'something I must do' feeling.

  \item Psychological triggers of certain external stimulai such as commercials, online browsing, telephone conversations, ect.
\end{enumerate}

Failure to understand and differentiate between these two distinct factors makes it difficult for PMOers to achieve success using the willpower method and is also the reason why many who do fall into the trap again. Although the withdrawal pangs of dopamine do not cause physical pain, do not underestimate their power. We talk of 'hunger pains' if we go without food for a day; there might be stomach rumbles, but there isn't any physical pain. Even so, hunger is a powerful force and we are likely to become very irritable when deprived of food. It is similar to when our body is craving a dopamine rush, the difference being that our body needs food, not poison. With the right frame of mind the withdrawal pangs are easily overcome and disappear very quickly.

After abstaining for a few days on the willpower method, the craving for dopamine flushes soon disappears. It's the second factor, brainwashing, that causes difficulty. The PMOer has gotten into the habit of relieving withdrawal pangs at certain times and occasions, which causes an association of ideas ("I got a hard on, so I must PMO." or "I am in bed with my laptop and I must PMO to feel happy"). The effect is best illustrated wih an example: You have a car and the indicator is on the left, on your next car it is on the right. You know it's on the right, but for a couple of weeks you put the windscreen wipers when you want to indicate.

Stopping PMO is similar, during the early days the trigger mechanism will operate at certain times. You will think about wanting to PMO, it is therefore essential to counter the brainwashing right from square one, causing these cues and triggers to quickly disappear. Under the willpower method, because the PMOer believes they are making a sacrifice, they are moping about it and waiting for the urge to go - far from removing these trigger mechanisms and actually increasing them. Similarly, under guru thinking the PMOer starts to wonder when they are going to become a God and even demands that they shouldn't have those thoughts, paving the way for self-loathing and failure.

A common trigger is alone time, particularly at a social event with friends. The ex-PMOer using other methods is already miserable due to being deprived of their usual crutch or pleasure. Their friends are with their partners and acting intimate. The PMOer is either single or not 'getting' any from their partner for whatever reason, now they are no longer enjoying what should be a pleasant social occasion. Their already made brain water slides lead them to porn, which is easier than either trying to woo their wife.

Because of the association of entitlement to sex with their well-being, they are now suffering a triple blow and the brainwashing is actually increased. If they are resolute and can hold out long enough they eventually accept their lot and get on with their life. However, part of the brainwashing still remains, the second most pathetic aspect being the PMOer who has quit but even after several years still craves 'just one last visit to the harem' on certain occasions. Pining for an illusion that exists only in their mind and is needlessly torturing themselves.

Even under EASYPEASY, responding to triggers is the most common failing. The ex-PMOer tends to regard internet porn as a sort of placebo or sugar pill. Thinking, "I know porn does nothing for me, but if I think it does then on certain occasions it will helpful." A sugar pill, although giving no actual physical help, can be a powerful psychological aid to relieve genuine symptoms and is therefore a benefit. Internet porn and habitual masturbation, however, aren't sugar pills. Why? Porn creates the symptoms it relieves and ceases to relieve them completely.

You may find it easier to understand the effect when related related to a non-PMOer or a succesful PMOer who has quit for several years. Take the case of a PMOer who loses their partner, it is quite common at such times, with the best of intentions, to say, "Have one harem visit, it will help calm you down." If the offer is accepted, it will not have a calming effect as there is no dopamine addiction and therefore no withdrawal pangs. At best, all it will do is give them a momentary psychological boost.

Even after the session is over, the original tragedy is there. In fact, it will be increased because the person is now suffering withdrawal pangs, the choice is now either to endure them or to relieve them by repeating the water slide rides to start the chain of misery all over again. All the porn provided was a fleeting psychological boost, the same that could have been achieved by a book or feel-good movie, even a bad one. Many non-PMOers and ex-PMOers have become re-addicted as a result of such occasions. Get it quite clear in your mind: You don't need the dopamine rush are are only torturing yourself further by continuing to regard it as some sort of prop or boost. There is no need to be miserable.

Orgasms do not make good relations; most times ruining them. Remember too that it is not entirely true that those who show public displays of affection are enjoying it at all times. Intimacy is best enjoyed in private where partners can respond without embarrassment, you don't have to be an orgasm induced dopamine addict. If it happens as a natural result of a series of life events, that's fine, but enjoy the occasion and life without it.

Abandoning the concept of PMOing as pleasurable in itself, many PMOers think "If only there was clean internet porn." There is clean soft porn, any PMOer who tries it soon finds out it's a waste of time. Get it clear in your mind that the only reason you have been PMOing is to get the dopamine flush. Once you have got rid of the dopamine craving for PMO you will ave no more need to visit your online harem.

Whether the pangs are due to actual dopamine withdrawal symptoms or trigger/cue mechanisms, accept it. The physical pain is non-existent and with the right frame of mind it will not be a problem. Do not worry about withdrawal, the feeling itself isn't bad. It's the association with wanting and then feeling denied that is the problem. Instead of moping about it, say to yourself "I know what it is, it's the withdrawal pang from PMO. That's what PMOers suffer their entire lives and what keeps them addicts. Non-PMOers don't suffer these pangs, it is another of the many evils of this lying addiction. It's it marvellous that I'm purging this evil from my brain."

In other words, for the next three weeks you will have a slight trauma inside your body, but during those weeks and for the rest of your life something marvellous wil be happening. You will be ridding yourself of an awful disease, the bonus will more than outweigh the slight trauma and you will actually be enjoying the withdrawal pangs. They will become moments of pleasure, like an exciting game to starve the PMO tape worm living inside your stomach. You have got to stave it for three weeks while it is trying to trick you into getting into bed to keep it alive.

At times, it will try to make you miserable. At times, you will be caught off-guard. You will receive a porn URL and forget that you have stopped, a slight feeling of deprivation when you remember. Be prepared for these tricks in advance, whatever the temptation, get it into your mind that it is only there because of the monster inside your body and every time you resist the temptation you have dealt another moral blow in the battle.

Whatever you do, don't try to forget about PMO. This is one the things that causes PMOers using the willpower method hours of depression. They try and get through each day hoping that eventually they'll just forget about it. It's like not being able to sleep, the more you worry about it, the harder it becomes. In any event, you won't be able to forget about it, for the first few days the 'little monster' will keep reminding you and you won't be able to avoid it. While there are still laptops, smartphones and magazines about you will have constant reminders.

The point being that you have no need to forget, nothing bad is happening. Something marvellous is happening, even if you are thinking about it a thousands times a day, \textbf{savor each moment, remind yourself of how marvelous it is to be free again. Remind yourself of the sheer joy of not having to torture yourself anymore.} As said previously, you will find that pangs become moments of pleasure, being surprised how quickly you will then forget about porn.

Whatever you do, \textit{do not doubt your decision}. Once you start to doubt, you will start to mope and it will get worse. Instead, use that moment of moping and convert it into a boost. If the cause is depression, then remind yourself that's what the PMO was doing to you. If you are forwarded a URL by a friend, take pride in saying, "I'm happy to say I don't need that anymore." This will hurt them, but when they see it isn't bothering you they will be halfway to joining you.

Remember that you had very powerful reasons for stopping in the first place. Remind yourself of the costs and ask yourself if you really want to risk malfunction of your body and mind. The most important loss being mental happiness and well-being, of not living under a spell. Be mindful of the little monster's efforts to minimise the hazards, above all, remember the feeling is only temporary and each moment is a moment closer to your goal.

Some PMOers fear they will have to spend the rest of their lives reversing the 'automatic triggers'. In other words, believing they will have to go through their lives kidding themselves they don't need PMO by use of psychology. This is not so, remember the optimist sees the bottle as half full and the pessimist sees it as half empty. In the case of PMO, the bottle is empty and the PMOer sees it as full. There are no advantages to using intenet porn and PMOing. It is the PMOer who has been brainwashed. Once you start telling yourself that you don't need to orgasm using PMO, in a very short time you won't even need to say it because the beautiful truth is that you don't need to PMO. It's the last thing you need to do; make sure it isn't the last thing you do.

\end{document}
