\documentclass[easypeasy.tex]{subfiles}
\chapter{Primary reasons for failure}
\begin{document}

There are two primary reasons for failure. The first is the influence of external stimulai - a commercial, online news article, internet browsing, ect. At a weak moment, or even during a social occasion somebody will get intimate with their partner. This topic has already been discussed at length. Use the moment to remind yourself there is no such thing as one visit or peek. Rejoice in the fact that you've broken the chain of mental slavery. Remember that the PMOer envies you and that you should feel pity for them, they need it.

The other primary reason is having a bad day, get it clear in your mind before you start that whether you're a PMOer and non-PMOer there are good and bad days. It rains for both the pope and the murderer. Life is relative and you can't have ups without downs. The issue with the willpower method is that as soon as the PMOer has a bad day they begin moping for a visit to the 'harem', further compounding the issue. The non-PMOer is better equipped, not only physically but mentally, to cope with stresses and strains. If you have a bad day during the withdrawal period just take it on the chin, reminding yourself that you had bad days when you were addicted, otherwise you wouldn't have decided to stop. Instead of moping about it, recognise it instead: \textit{"Okay, so today's not so good but PMO won't cure it. Tomorrow will be better and at least I've got a marvellous bonus, I've kicked that awful PMO addiction."}

When you're a PMOer you have to block your mind to the negatives of PMO. PMOers never have brain fog, they're just 'a bit down'. When you're having life's inevitable troubles you want to PMO, but are you happy and cheerful? Of course you aren't. Once you stop, the tendency is to blame everything that goes wrong on the fact that you have stopped.

If work stresses you out, you think, \textit{"At times like this I would have PMOed."} This is true, but the important thing that's forgotten is that PMO didn't solve the problem and you're simply punishing yourself by moping for an illusory crutch. You're creating an impossible situation, you're miserable because you can't have the porn and masturbation, yet you'll be even more miserable if you do. You know that you've made the correct decision by stopping PMO, so why punish yourself by doubting your decision?

{\Large Remember, a positive mental approach is essential - always.}

\end{document}
